---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# CalcRelAb

<!-- badges: start -->
<!-- badges: end -->

The goal of CalcRelAb is to easily manipulate phyloseq objects for graphing useful information in R. This relies heavily on the functionality and data in the [phyloseq package by joey711](https://joey711.github.io/phyloseq/).

While the phyloseq datatype is full of information, it does not parse naturally into ggplot, nor does it contain / allow for calculation of relative abundance values. This package contains the function calc_relative_abundance() which first uses the phyloseq function psmelt() to convert a phyloseq object into a simple R dataframe. It then appends a column onto the dataframe containing the relative abundance of each OTU for its sample.

The package also contains data from the phyloseq package, saved and documented in the /data directory.

## Installation

You can install the development version of CalcRelAb like so:

``` r
install_github("stat545ubc-2024/CalcRelAb", build_vignettes = TRUE, ref = "0.1.0")
```

## Example

This is a basic example. We are using the esophagus phyloseq object that comes with the phyloseq package, and is contained within our data. This is passed through our calc_relative_abunance() function. 

We can see that a column has been created called "Relative_Abundance".

```{r example}
library(CalcRelAb)
library(phyloseq)
library(tidyverse)

data("esophagus")
calc_relative_abunance(esophagus)
```

