---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# CalcRelAb

<!-- badges: start -->
<!-- badges: end -->

The goal of CalcRelAb is to easily manipulate phyloseq objects for graphing useful information in R. 
While the phyloseq datatype is full of information, it does not parse naturally into ggplot, nor does it contain / allow for calculation of relative abundance values. This package contains the function calc_relative_abundance() which first uses the phyloseq function psmelt() to convert a phyloseq object into a simple R dataframe. It then appends a column onto the dataframe containing the relative abundance of each OTU for its sample.

## Installation

You can install the development version of CalcRelAb like so:

``` r
install_github("org/repo", build_vignettes = TRUE, ref = "0.1.0")
```

## Example

This is a basic example. We are using the soilrep phyloseq object that comes with the phyloseq package. This is passed through our calc_relative_abunance() function. 

We can see that a column has been created called "Relative_Abundance".

```{r example}
library(CalcRelAb)
library(phyloseq)
data("esophagus")
calc_relative_abunance(esophagus)
```

